\section{Methodology}
\subsection{Description}
\noindent\fbox{
	\parbox{\textwidth}{
		\textbf{1.} Define a methodology$^1$ using SysML/UML diagrams for the development of your system. Specify SysML/UML diagrams that need to be made in the different phases of the project. Make a short description of each design phases and the SysML/UML diagrams and profiles you decide to use in the methodology. Remember to use references to the papers you have use as inspiration for your work. Decide on an UML$^2$ tool.
	}
}\citepawesome{Bjerge2017}{1}


\subsection{SysML}
In this project SysML standard will be used to describe the system as a whole, but also to help describe core functionality down to the wire. The usage of SysML standard is decided upon because of the structural approach to the analysis. To ensure cohesion throughout the usage of SysML and UML, the "A Practical Guide to SysML: The Systems Modeling Language"\cite{Friedenthal2014} document will be used. This report will follow a Top-Down approach as stated below:

\begin{itemize}
	\item Analyzing the Problem
	\item Model Organization
	\item Operation
	\begin{itemize}
		\item Use Cases
		\item Requirements
	\end{itemize}
	\item Structure
	\begin{itemize}
		\item Block Definition Diagram (bdd)
		\item Internal Block Diagram (ibd)
	\end{itemize}
	\item Behavior
	\begin{itemize}
		\item Sequence Diagram (sd)
		\item Activity Diagram (act)
		\item State Machine Diagram (smd)
	\end{itemize}
\end{itemize}


Microsoft Visio will be used as a UML tool with the included stencil toolbox\citeawesome{Hruby2018}.

\input{methodology/analyzingtheproblem/analyzingtheproblem}
\input{methodology/modelorganization/modelorganization}
\input{methodology/operation/operation}
\input{methodology/structure/structure}
\input{methodology/behavior/behavior}






