\section{Implement and Test}

\subsection{Description}

\noindent\fbox{
	\parbox{\textwidth}{
		\textbf{5.} Select the SysML/UML model for your preferred architecture suggestions in \textbf{3.} Choose a part of the functionality including both hardware and software components to create a model and a testbench in HLS using SystemC or C-code. Simulate and validate your design model. \\\\
		Argue for your choice of modeling language and abstraction level of modeling. Use the reports from the HLS tool to evaluate performance of the design. Assess whether the design is able to fulfill your requirements and constraints.
	}
}\citepawesome{Bjerge2017}{2}
\\\\

This description is for the implementation itself and it is split into two subsections. One with Verdado and the other have 

\subsection{Verdado}
This section will show the Verdado design on the board including console outputs. Our design makes use the GPIO ports to access the hardware buttons and switches. The buttons are used to control the actions in the application ActionUp, ActionDown, ActionNext and ActionStart. The switches are used to control the different states the PSOS can be in Setup, FindMinima and FindMaxima.

INSERT IMAGE OF BLOCK DIAGRAM FROM Verdado!!!!!!

The Software is made using FreeRTOS, where the mainThread controls the application. As it can be seen below it initializes the buttons and switches.

\begin{lstlisting}[style=customc++, label={lst:listingExample}, caption={Example listing.}]
#include <stdio.h>
#define N 10
/* Block
* comment */
{

INSERT CODEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEE

}
\end{lstlisting}

As menshioned in section \ref{designpatterns} the gof state patteren is used. The context can be seen below.
\begin{lstlisting}[style=customc++, label={lst:listingExample}, caption={Example listing.}]
#include <stdio.h>
#define N 10
/* Block
* comment */
{

INSERT CODEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEEE

}
\end{lstlisting}

The states is an important part of this patterens therefore an example of the setup state can be seen here. To make the code easier to read it is clearly split into actions and transitions. 


\subsection{Vedado HLS}

\subsection{Description}

\noindent\fbox{
	\parbox{\textwidth}{
		\textbf{6.} Implement and test a part of your system using the ZYBO platform including at least one IP core written and verified with the HLS tool.
	}
}\citepawesome{Bjerge2017}{2}